Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-05-11 PAPER.tex
minor syntax edit

The second null test possibility (error bars consistent with zero but not with thermal noise) is displayed by the $k$-values just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) for all three tests. This indicates an additive noise component that is increasing our errors. More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power. This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term. When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise. While the cross-terms have a mathematical expectation value of zero, in practice we are limited by our number of samples ($90$ cross-products for this analysis times $\sim$ $8$ independent LST samples). Combined with the fact that the foregrounds are so bright, these couplings can introduce extra variance that would vary with foreground strength. It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.

>>>>

The second null test possibility (error bars consistent with zero but not with thermal noise) is displayed by the $k$-values just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) for all three tests. This indicates an additive noise component that is increasing our errors. More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power. This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term. When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise. While the cross-terms have a mathematical expectation value of zero, in practice we are limited by our number of samples ($90$ cross-products for this analysis times $\sim$ $8$ independent LST samples). Combined with the fact that the foregrounds are so bright, the finite ensemble of the couplings can introduce extra variance that varies with foreground strength. It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.
